An Expanded Search for Supernova Remnants in NGC\,6946

### 2018-12-12 ms.tex
Per requests from Bill and Frank, additional figures have been added which show the run of several line ratios with GC distance

\todo[inline]{Bill and Frank point out that various other diagrams with GC radius are missing, and in particular \sii:\ha\ ratio vs. \ha\ flux; \sii:\ha\ ratio vs. GCD (fig for this already here)  Check M83 to see if there is a correlation in the spectroscopic ratio with GCD, and if so comment on this.  This is done for S2; I guess we could to it for N2. Gradients: \nii:\ha\ and \sii:\ha\ vs GCD (M83 paper, fig 8) [WPB: Yes, I'd definitely like to see what this looks like.]}

@@

>>>>

\todo[inline]{Bill and Frank point out that various other diagrams with GC radius are missing, and in particular \sii:\ha\ ratio vs. \ha\ flux; \sii:\ha\ ratio vs. GCD (fig for this already here)  Check M83 to see if there is a correlation in the spectroscopic ratio with GCD, and if so comment on this.  This is done for S2; I guess we could to it for N2. Gradients: \nii:\ha\ and \sii:\ha\ vs GCD (M83 paper, fig 8) [WPB: Yes, I'd definitely like to see what this looks like.].  ksl: This is now provided, but whether these should be included is open to question.  If they are included some massaging of the plots is needed.  If included, Bill or Frank should provide words, and comparison to other galaxies}

Some of the line ratios show indications of a metallicity gradient as evidenced in Fig. \ref{fig_metal_ratios}.  However, unlike the case in M33, what is seen in both the N2:Ha and S2:Ha ratio is that the upper envelope of both plots decreases with radius, but there are examples of SNRs with low ratios at all GC radii.

@@

\begin{figure}
\plottwo{fig_n2_ha_gc.pdf}{fig_s2_ha_gc.pdf}
\caption{Line ratios as a function of GC distance \label{fig_metal_ratios}}
